\documentclass{beamer}

\usetheme{Madrid}

\title{UrbanClap Service Platform}
\author{Tarun kumar, Vansh, Atif, Himanshu}

\institute{MERN Stack Project}
\date{\today}

\begin{document}

% Title Slide
\begin{frame}
\titlepage
\end{frame}

% Slide 1
\begin{frame}{Brief About the Project}
The UrbanClap Service Platform is a web application developed using the MERN Stack (MongoDB, Express.js, React.js, Node.js).

The main goal of the project is to connect users with service providers easily.

Users can register on the platform and choose the type of services they require such as home cleaning, plumbing, electrical repair, and other household services.

The platform provides a simple interface where users can explore services, book appointments, and manage their service requests online.
\end{frame}

% Slide 2
\begin{frame}{Comparison with Existing Systems}

Traditional service booking methods usually involve contacting service providers manually which can be time consuming.

Existing online platforms sometimes lack a simple user interface and proper service categorization.

Our system improves the process by providing:
\begin{itemize}
\item Easy user registration and login
\item Service categorization
\item Quick booking system
\item User-friendly interface
\end{itemize}

This makes the process faster and more convenient for users.
\end{frame}

% Slide 3
\begin{frame}{Tools Used for the Project}

The project is developed using the MERN Stack.

\begin{itemize}
\item MongoDB – Database to store user and service data
\item Express.js – Backend framework
\item React.js – Frontend user interface
\item Node.js – Server side environment
\item Visual Studio Code – Code editor
\item Git and GitHub – Version control
\end{itemize}

These tools help in building a scalable and efficient web application.
\end{frame}

% Slide 4
\begin{frame}{Timeline of the Project}

The project development is divided into several phases.

\begin{itemize}
\item Week 1 – Requirement analysis and project planning
\item Week 2 – UI design and frontend development
\item Week 3 – Backend development and database setup
\item Week 4 – Integration of frontend and backend
\item Week 5 – Testing and debugging
\item Week 6 – Final deployment and documentation
\end{itemize}

This structured timeline helps in completing the project efficiently.
\end{frame}

% Slide 5
\begin{frame}{Status of Work Done}

Currently the following parts of the project have been completed:

\begin{itemize}
\item User registration and login system
\item Service listing section
\item Basic user interface using React
\item Backend API creation using Node.js and Express
\item Database connection using MongoDB
\end{itemize}

Remaining work includes improving UI design, adding booking functionality, and performing testing before final deployment.
\end{frame}

\end{document}